Alignment Statistic
========================================================


```{r carrega, echo=FALSE, results='hide',warning=FALSE,error=FALSE, message=FALSE}
source("Scripts/Auxiliar.R")
source("Scripts//CreaScores.R")
source("Scripts//Imprimir.R")
load("BEC.RData")
dades =read.table("Dades.txt")
info =read.csv("Files/Nets/Info_Nets.txt", sep ="\t")

nom1 = as.character(dades[1,1])
nom2 = as.character(dades[2,1])
net1 = paste("Files/Nets/",nom1,"Adria.txt",sep="")
net2 = paste("Files/Nets/",nom2,"Adria.txt",sep="")
#piswapEC=0
#pints2EC=pints2FC=pints2TM=0
#pints2EC=pints2FC=pints2TM=0
#creaScore(nom1,nom2)
scores = paste("Results/Scores2",nom1,nom2,".RData",sep="")
load(scores)
pintsEC=pintsEC-BEC$PINTS[nom1,nom2]
netalEC=netalEC-BEC$NETAL[nom1,nom2]
isoEC=isoEC-BEC$ISORANK[nom1,nom2]

#if(piswapEC==0){
 #creaScore2(nom1,nom2)
#load(scores)

#}

```


```{r , echo=FALSE,results='hide'}
info1=info[which(info$Xarxa==nom1),]
info2=info[which(info$Xarxa==nom2),]

```
First Network 

Information:
  * Specie: `r info1$Especie`
  * Common name: `r info1$Comu`
  * Data base: `r info1$DB`
  * Date: `r info1$Data`
  
Statistics:
  * Nodes: `r info1$Nodes`
  * Edges: `r info1$Arestes`
  * Diameter: `r info1$Diametre`
  * InteractionFC: `r info1$AutoFC`
  
Second Network 

Information:
  * Specie: `r info2$Especie`
  * Common name: `r info2$Comu`
  * Data base: `r info2$DB`
  * Date: `r info2$Data`
  
Statistics:
  * Nodes: `r info2$Nodes`
  * Edges: `r info2$Arestes`
  * Diameter: `r info2$Diametre`
  * InteractionFC: `r info2$AutoFC`

SCORES


```{r ,echo=FALSE,results='asis'}
ccc = c("ECScore","FCScore","TMScore")
fff = c("PINTS","ISORANK","NETAL")
mmm = matrix(c(pintsEC,pintsFC,pintsTM,isoEC,isoFC,isoTM,netalEC,netalFC,netalTM),nrow=3,byrow=TRUE)
mmm=as.table(mmm)
dimnames(mmm) = list(fff,ccc)
kable(mmm,format='html')
```


```{r , echo=FALSE}
#, names.arg=c("PEC","P2EC","P3EC","P4EC","IPEC","IEC","NEC","PFC","IPFC","P2FC","IFC","PTM","IPTM","P2TM","ITM")
mat = matrix(c(pintsEC,pintsFC,pintsTM,isoEC,isoFC,isoTM,netalEC,netalFC,netalTM),nrow=3,byrow=TRUE)
barplot(mat,col=c("darkgreen","darkred","black"), ylim=c(0,1), beside=TRUE)
```

