README
========================================================
<h2>First case</h2>
First we will see a little artificial example to see how to use the program

First load the script avaliable in "http://bass.uib.es/~ppin/Scripts/PINTS.R"
```{r loadPINTS}
source("http://bass.uib.es/~ppin/Scripts/PINTS.R")

```

Then you have to create the networks and the similarity matrix, the format of the networks must be list of edges separated by tab and the similirity matrix must be a list of values, i. e.

<pre>node_network1\tnode_network2\tvalue</pre>

You can found a little example of networks and similarity matrix in http://bass.uib.es/~ppin/Files/Example

Finally we can execute the program
```{r loadExample,results='hold'}
net1 = "http://bass.uib.es/~ppin/Files/Example/NetExample1.txt"
net2 = "http://bass.uib.es/~ppin/Files/Example/NetExample2.txt"
similarity.matrix = "http://bass.uib.es/~ppin/Files/Example/SimilarityMatrixExample.txt"
alin = pints(net1,net2,similarity.matrix,verbose=TRUE)
alin
```

If the networks are small you can see the alignment
```{r plotExample}
source("http://bass.uib.es/~ppin/Scripts/Auxiliar.R")
source("http://bass.uib.es/~ppin/Scripts/plotAlignment.R")

Gnet1 = makeGnet(net1)
Gnet2 = makeGnet(net2)
plotGraph(Gnet1,color='green')
plotGraph(Gnet2,color='red')
plotAlignment(Gnet1,Gnet2,alin)
```

Now we have the alignment we can calculate the ECScore, for this we need two more scripts (avaliables in http://bass.uib.es/~ppin/Scripts)
```{r ECExample,message=FALSE}
source("http://bass.uib.es/~ppin/Scripts/CreaScores.R")
ECscore(Gnet1,Gnet2,alin)

```

<h2>Real case 1</h2>

First load all necessary scripts
```{r loadPINTS2, message=FALSE}
source("http://bass.uib.es/~ppin/Scripts/PINTS.R")
source("http://bass.uib.es/~ppin/Scripts/CreaScores.R")
source("http://bass.uib.es/~ppin/Scripts/Auxiliar.R")

```

Calculate the alignment, net1, net2 and similarity.matrix must be directories.

```{r loadReal1,results = 'markup',eval=FALSE}
net1 = "http://bass.uib.es/~ppin/Files/Nets/RnorvAdria.txt"
net2 = "http://bass.uib.es/~ppin/Files/Nets/HpyloAdria.txt"
similarity.matrix = "http://bass.uib.es/~ppin/Files/matrius/RnorvHpylo.blast"

alin = pints(net1,net2,similarity.matrix)
```

```{r loadReal11,echo=FALSE, results='hide'}
net1 = "http://bass.uib.es/~ppin/Files/Nets/RnorvAdria.txt"
net2 = "http://bass.uib.es/~ppin/Files/Nets/HpyloAdria.txt"
similarity.matrix = "http://bass.uib.es/~ppin/Files/matrius/RnorvHpylo.blast"
load("Results/AlinRnorvHpylo.RData")
```

The alignment is a two-column table, like this
```{r headAlin1}
head(alin)
```
In this case we barely see anything
```{r plotReal1}
Gnet1 = makeGnet(net1)
Gnet2 = makeGnet(net2)
plotGraph(Gnet1,color='green')
plotGraph(Gnet2,color='red')
plotAlignment(Gnet1,Gnet2,alin)

```

Once you have the alignment you can calculate several scores, for example, ECScore
```{r ECReal1,message=FALSE }
ECscore(Gnet1,Gnet2,alin)
```

Finally if your proteins are in DIP format you can calculate the FCscore
```{r FCReal1}
specie1 = "Rnorv"
specie2 = "Hpylo"
FCScore(alin,specie1,specie2)
```

The species avaliables are Rnorv,Hpylo, Mmusc, Cel, Eco, Hsapi, sce and Dme ( you can found information about the PPIN of this species in http://bass.uib.es/~ppin/Info)

<h2>Real case 2</h2>

First load all necessary scripts
```{r loadPINTS3, message=FALSE}
source("http://bass.uib.es/~ppin/Scripts/PINTS.R")
source("http://bass.uib.es/~ppin/Scripts/CreaScores.R")
source("http://bass.uib.es/~ppin/Scripts/Auxiliar.R")

```

Calculate the alignment, net1, net2 and similarity.matrix must be directories.

```{r loadReal2,results = 'markup',eval=FALSE}
net1 = "http://bass.uib.es/~ppin/Files/Nets/sceAdria.txt"
net2 = "http://bass.uib.es/~ppin/Files/Nets/DmeAdria.txt"
similarity.matrix = "http://bass.uib.es/~ppin/Files/matrius/sceDme.blast"

alin = pints(net1,net2,similarity.matrix)
```

```{r loadReal21,echo=FALSE, results='hide'}
net1 = "http://bass.uib.es/~ppin/Files/Nets/sceAdria.txt"
net2 = "http://bass.uib.es/~ppin/Files/Nets/DmeAdria.txt"
similarity.matrix = "http://bass.uib.es/~ppin/Files/matrius/sceDme.blast"
load("Results/AlinsceDme.RData")
```

The alignment is a two-column table, like this
```{r headAlin2}
head(alin)
```
In this case we see anything
```{r plotReal2}
Gnet1 = makeGnet(net1)
Gnet2 = makeGnet(net2)
plotGraph(Gnet1,color='green')
plotGraph(Gnet2,color='red')
plotAlignment(Gnet1,Gnet2,alin)

```

Once you have the alignment you can calculate several scores, for example, ECScore
```{r ECReal2,message=FALSE }
ECscore(Gnet1,Gnet2,alin)
```

Finally if your proteins are in DIP format you can calculate the FCscore
```{r FCReal2}
specie1 = "sce"
specie2 = "Dme"
FCScore(alin,specie1,specie2)
```
